Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-26 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimse a queue of task related services that is decoded into composition solutions. We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.

@@

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic dimension enables a better underrstanding and collaboration through ontology-based semantics \cite{o2005review}. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services. The second challenge is related to finding optimised solutions in QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.

@@

 \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our propopsed model with one widely used QoS model using PSO-based approach. In addtion, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model. Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimization and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

@@

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimse semantic matchmaking quality and QoS simultaneously. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository. These web services provide different QoS in terms of availability, price, reliability and response time. Moreover, valid semantic matches between two connected web services could also have different matchmaking quality. For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$. The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem. For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa. To demonstrate the motivation of proposing a comprehensive quality, we give a simple example. The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") availabile in the service repository. This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS. Therefore, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.

@@

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in serveral models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.

@@

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$.
\vspace{0.3cm}

@@

We use the returns of $type(a, b)$ to define a full matchmaking considerd in the scenario of connecting two services through concept-related output and concept-related input.

@@

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q(a \Rightarrow b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
\vspace{0.3cm}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task related services that is decoded into composition solutions. We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.

@@

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic dimension enables a better understanding and collaboration through ontology-based semantics \cite{o2005review}. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services. The second challenge is related to finding optimised solutions in QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.

@@

 \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our proposed model with one widely used QoS model using PSO-based approach. In addition, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model. Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybrid approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

@@

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository. These web services provide different QoS in terms of availability, price, reliability and response time. Moreover, valid semantic matches between two connected web services could also have different matchmaking quality. For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$. The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem. For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa. To demonstrate the motivation of proposing a comprehensive quality, we give a simple example. The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository. This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS. Therefore, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.

@@

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.

@@

\textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$.
\vspace{0.3cm}

@@

We use the returns of $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.

@@

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
\vspace{0.3cm}
